25 years of Social Work Research

### 2015-03-22 dataCleaning.Rmd
Updated analyses. Everything working.

# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)

@@

plot.article.count <- ggplot(articles.year.df, aes(as.factor(years), 
                    y = year.count, group=1)) + 
    geom_line(colour="black") +
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Articles") + 
    ggtitle("A. Number of Articles by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(breaks = c(seq(0, 2500, 200))) +
    annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
             ymin = 1700, ymax = 2050, alpha = .20, fill = "red") +
      annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
             ymin = 1400, ymax = 1750, alpha = .20, fill="red")  
```

@@

plot.journal.count <- ggplot(n.journals.year, aes(as.factor(record.y), 
                    y = Journal.count, group=1)) + 
    geom_line(colour="black") +
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    ggtitle("B. Number of Journals by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) +
     annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
             ymin = 55, ymax = 70, alpha = .20, fill="red") +
         annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
             ymin = 53, ymax = 62, alpha = .20, fill = "red")  
```

@@

plot.author.count <- ggplot(n_authors, aes(as.factor(pubYear), y=average.n, group=1)) +  
    #geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), colour="lightblue", fill="lightblue", alpha=.40) +
    #geom_line(colour="black") + 
    geom_point() +
    geom_line() + 
    ylab("Authors") +
    xlab("Year") +
    ggtitle("Average Number of Authors per Article by Year") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), 
          plot.title = element_text(size = 10), 
          title = element_text(size = 10)) + 
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) + 
    scale_y_continuous(limits = c(0,3))
```

```{r locationExtraction}
LO.df <- filter(full.df, attributes == "location") %>%
         group_by(record) %>%
         summarise(Country = unique(record),
                   N = n()) %>%
        arrange(desc(N)) %>% 
        select(-record)

@@

```{r locationWithoutUS}
year.df <- filter(full.df, attributes == "pubYear") %>%
            select(articleID, record)

location.summary.df <- group_by(year.location.df, country) %>%
           summarize(Number = n()) %>%
           arrange(desc(Number)) %>%
           slice(2:6) %>%
           select(country)

location.df <- location.df[location.df$record %in% location.summary.df$country, ]
year.location.df <- left_join(location.df, year.df, by = "articleID") 
colnames(year.location.df) <- c("articleID", "country", "pubYear")
year.location.df.noUS <- group_by(year.location.df, country, pubYear) %>%
                    summarise(N = n())

@@

```{r plotLocationWithUS}
plot.location.withUS <- ggplot(year.location.df, aes(pubYear, N, group = country, colour=country)) + 
    geom_line() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(size = 10)) +
    scale_y_continuous(limits = c(0,600)) + 
    xlab("Year") +
    ylab("Articles") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) + 
    ggtitle("Number of Articles by Country and Year")
```

```{r}
nsf <- data.frame(c(238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280), as.factor(seq(2002,2012, 1)))
colnames(nsf) <- c("n.grads", "years")
```

```{r}
plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
    geom_line(linetype="dotted") + 
    geom_point() +
     scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
     ylab("Doctoral degrees") +
     xlab("Year") +
     geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(size = 10)) +
     ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
```

>>>>

# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)

@@

plot.article.count <- ggplot(articles.year.df, aes(as.factor(years), 
                    y = year.count, group=1)) + 
    geom_line(colour="black") +
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Articles") + 
    ggtitle("A. Number of Articles by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(breaks = c(seq(0, 2500, 200))) +
    annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
             ymin = 1700, ymax = 2050, alpha = .20, fill = "#0072B2") +
      annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
             ymin = 1400, ymax = 1750, alpha = .20, fill= "#0072B2")  
```

@@

plot.journal.count <- ggplot(n.journals.year, aes(as.factor(record.y), 
                    y = Journal.count, group=1)) + 
    geom_line(colour="black") +
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    ggtitle("B. Number of Journals by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) +
     annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
             ymin = 55, ymax = 70, alpha = .20, fill= "#0072B2") +
         annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
             ymin = 53, ymax = 62, alpha = .20, fill = "#0072B2")  
```

@@

n_authors2 <- n_authors%>% 
       select(median.n, average.n, std.dev) %>%
       rename(median = median.n, average = average.n)

n_authors2$ID <- as.factor(c(1989:2013))

n_authors2_melted <- reshape2::melt(n_authors2, id.vars = "ID")
colnames(n_authors2_melted) <- c("pubYear", "summaryStat", "value")

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

plot.author.count <- ggplot(n_authors2_melted, aes(x = pubYear, y = value, group = summaryStat, colour = summaryStat)) + 
     geom_line(size = .75) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          title = element_text(size = 10), 
          legend.title=element_blank()) +
    scale_colour_manual(values=cbPalette)  +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(0,2.5)) +
    ylab("Value") +
    xlab("Year") +
    ggtitle("Authors Per Article by Year")

@@

```{r locationExtraction}
LO.df <- filter(full.df, attributes == "location") %>%
         group_by(record) %>%
         summarise(Country = unique(record),
                   N = n()) %>%
        arrange(desc(N)) %>% 
        select(-record)
```

```{r locationExtraction2}
LO.df2 <- filter(full.df, attributes == "location" | attributes == "abstract" |
                 attributes == "article" | attributes == "keyword")
indx.country <- paste(countries.csv$x, collapse = "|")
library(stringi)
countries.extracted <- na.omit(within(LO.df2, text1<- stri_extract(LO.df2$record, regex=indx.country)))[-2]
country.indexed <- as.numeric(rownames(countries.extracted))
location.ID <- LO.df2$articleID[country.indexed]

detach(package:stringi)
```

@@

```{r plotLocationWithUS}

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

plot.location.withUS <- ggplot(year.location.df, aes(pubYear, N, group = country, colour=country)) + 
    geom_line() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          title = element_text(size = 10), 
          legend.title=element_blank())  +
    scale_y_continuous(limits = c(0,600)) + 
    xlab("Year") +
    ylab("Articles") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) + 
    scale_colour_manual(values=cbPalette) +
    ggtitle("Number of Articles by Country and Year")
```

```{r nsf}
nsf <- data.frame(c(238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280), as.factor(seq(2002,2012, 1)))
colnames(nsf) <- c("n.grads", "years")
```

```{r nsfPlot}
plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
    geom_line(linetype="dotted", colour = "#0072B2", size = .75) + 
    geom_point(colour = "#0072B2", size = .75) +
     scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
     ylab("Doctoral degrees") +
     xlab("Year") +
     geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1), 
           title = element_text(size = 10)) +
     ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
```
